14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-16 rules/rules19.tex
Rules: Update changes with benchmark selection info.

  \item {\bf Benchmark Selection.} \todo{}

>>>>

  \item {\bf Benchmark Selection.} Since 2015, the competition evaluated all
    solvers on all eligible benchmarks in SMT-LIB.  This year, we will use an
    alternative benchmark selection scheme that selects a subset of the
    eligible benchmarks. The upper bound for the size of each division,
    however, is not fixed, but depends on the size of the corresponding logic.
    Prior to this selection, we will remove all benchmarks in a division that
    were solved by all solvers (including non-competing solvers) in this
    division in under a second during last year's competition.
    \rationale{Evaluating solvers on all eligible benchmarks in SMT-LIB makes
    results more predictable and seems to be more of an evaluation than a
    competition.  In the Main track of last year's competition, 78\% of the 258,741
    benchmarks were solved by all supported solvers within the time
    limit (71\% within 1 second). In 7 (out of 46) logics, over 99\% of
    benchmarks were solved by all solvers.  Removing `easy' (or at least
    `unsurprising') benchmarks attempts to shift the focus towards challenging
    benchmarks, in particular since we now use an alternative benchmark
    selection scheme.  It can be argued that the size of a logic in SMT-LIB can
    be seen as an indicator of its relevance.  We thus do not use a fixed upper
    bound for the size of a division in order to reflect the suggested
    importance of a division.}
